Tourism Data Analysis

### 2019-08-27 Application-R/Application-TourismData/Final-results/TourismData-Final-results.Rmd

OvernightTrips_OriginalScale_Fc %>% 
  mutate(SquaredE = (Overnight_Trips - Overnight_Trips_Fc)^2) %>% 
  group_by(`R.method`, Fc_horizon, Replication) %>% 
  summarise(MSE = mean(SquaredE)) -> OvernightTrips_OriginalScale_MSE

DF_MSE <- DF_LogTrans %>%
  mutate(SquaredE = (`Actual` - `Forecasts`)^2) %>%
  filter(`Forecast_Horizon` == 1) %>%
  dplyr::select(-`Forecast_Horizon`) %>%
  group_by(`F.method`, `R.method`, Replication) %>%
  summarise(MSE = mean(SquaredE))

DF_MSE %>%
  filter(`F.method`=="Unbiased_M1", `R.method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS")) %>%
  spread(key = `R.method`, value = MSE) %>%
  mutate("Base-OLS" = Base - OLS,
         "Base-MinT" = Base - `MinT(Shrink)`,
         "Base-WLS" = Base - WLS) %>%
  dplyr::select(Replication, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>%
  rename("OLS" = "Base-OLS", "MinT" = "Base-MinT", "WLS" = "Base-WLS") %>%
  gather(`OLS`, `WLS`, `MinT`,  key = Method, value = MSE) %>%
  mutate(Method = factor(Method, levels = c("OLS", "MinT", "WLS"))) %>%
  ggplot(aes(x = Method, y = MSE)) +
  geom_boxplot() +
  ylab("MSE") + xlab("Reconciliation Method")

>>>>

OvernightTrips_OriginalScale_Fc %>% 
  mutate(SquaredE = (Overnight_Trips - Overnight_Trips_Fc)^2, 
         Fc_horizon = recode(Fc_horizon, "1" = "h=1", "2" = "h=2",
                             "3" = "h=3", "4" = "h=4", "5" = "h=5", "6" = "h=6")) %>% 
  group_by(`R.method`, Fc_horizon, Replication) %>% 
  summarise(MSE = mean(SquaredE)) -> OvernightTrips_OriginalScale_MSE

OvernightTrips_OriginalScale_MSE %>%
  filter(`R.method`%in% c("Base", "OLS", "MinT(Shrink)", "WLS")) %>%
  spread(key = `R.method`, value = MSE) %>%
  mutate("Base-OLS" = Base - OLS,
         "Base-MinT" = Base - `MinT(Shrink)`,
         "Base-WLS" = Base - WLS) %>%
  dplyr::select(Fc_horizon, Replication, `Base-OLS`, `Base-MinT`, `Base-WLS`) %>%
  rename("OLS" = "Base-OLS", "MinT" = "Base-MinT", "WLS" = "Base-WLS") %>%
  gather(`OLS`, `WLS`, `MinT`,  key = Method, value = MSE) %>%
  mutate(Method = factor(Method, levels = c("OLS", "MinT", "WLS"))) %>%
  ggplot(aes(x = Method, y = MSE)) +
  geom_boxplot() + facet_wrap(~ Fc_horizon) +
  ylab("MSE") + xlab("Reconciliation Method")
